---
title: "TIE_Results_actualized"
format: html
---
```{r, echo=FALSE}
options(scipen = 999)
library(plm)
library(dplyr)
library(ggplot2)
library(rstudioapi)
library(tidyr)
library(knitr)
library(kableExtra)
library(readr)
library(gridExtra)
library(lubridate)
library(readxl)
library(xfun)
library(rmarkdown)
library(haven)
library(ggplot2)
library(stargazer)
library(modelsummary)
library(webshot2)
library(lme4)
library(sandwich)
library(lmtest)
library(betareg)
library(car)
library(stringr)
library(summarytools)
```
### Attitudes towards the EU (Euroscepticism)
```{r, echo=FALSE}
full_data_euroscepticism_demo <- read_csv("full_data_euroscepticism_demo.csv")
eu_proposals_data <- read_csv("eu_proposals_dataset.csv")
```
```{r, echo=FALSE}
full_data_euroscepticism_demo <- full_data_euroscepticism_demo|>
  mutate(
    age_group = floor(Age / 5) * 5,
    age_group_label = paste0(age_group, "-", age_group + 4))

full_data_euroscepticism_demo <- full_data_euroscepticism_demo|>
  mutate(cohort_id = Country)

full_data_euroscepticism_demo <- full_data_euroscepticism_demo|>
mutate(euroscepticism = if_else(`EU_membership_good-bad` == 2, 1, 0))

full_data_euroscepticism_demo <- full_data_euroscepticism_demo|>
mutate(EU_not_benefit = if_else(`EU_membership_country_benefit` == 2, 1, 0))

pseudo_panel_aggregated <- full_data_euroscepticism_demo|>
  group_by(cohort_id, Year)|>
  summarize(
    euroscepticism = weighted.mean(euroscepticism, weight, na.rm = TRUE),
    EU_not_benefit = weighted.mean(EU_not_benefit, weight, na.rm = TRUE),
    `Trade balance of goods` = mean(`Trade balance of goods`, na.rm = TRUE),
    `FDI net balance` = mean(`FDI net balance`, na.rm = TRUE),
    `Ratio of migrant to native workers` = mean(`Ratio of migrant to native workers`, na.rm = TRUE),
    .groups = "drop")

pseudo_panel_aggregated <- pseudo_panel_aggregated %>%
  mutate(
    Trade_balance_scaled = `Trade balance of goods` / 1e6,
    FDI_net_balance_scaled = `FDI net balance` / 1e6)

pseudo_panel_data <- pdata.frame(pseudo_panel_aggregated, index = c("cohort_id", "Year"))

pseudo_panel_data <- pseudo_panel_data |>
  mutate(Year = as.numeric(as.character(Year)))
```
```{r, echo=FALSE}
eu_proposals_data <- eu_proposals_data|>
  mutate(cohort_id = Country)

eu_proposals_data <- eu_proposals_data|>
mutate(Single_currency = if_else(Single_currency == 2, 1, 0))

eu_proposals_data <- eu_proposals_data|>
mutate(Common_foreign_policy = if_else(Common_foreign_policy == 2, 1, 0))

eu_proposals_data <- eu_proposals_data|>
mutate(Common_defence_policy = if_else(Common_defence_policy == 2, 1, 0))

eu_proposals_data <- eu_proposals_data|>
mutate(Common_migration_policy = if_else(Common_migration_policy == 2, 1, 0))

eu_proposals_data <- eu_proposals_data|>
mutate(Common_trade_policy = if_else(Common_trade_policy == 2, 1, 0))

eu_proposals_pseudo_panel_aggregated <- eu_proposals_data|>
  group_by(cohort_id, Year)|>
  summarize(
    Single_currency = weighted.mean(Single_currency, weight, na.rm = TRUE),
    Common_foreign_policy = weighted.mean(Common_foreign_policy, weight, na.rm = TRUE),
    Common_defence_policy = weighted.mean(Common_defence_policy, weight, na.rm = TRUE),
    Common_migration_policy = weighted.mean(Common_migration_policy, weight, na.rm = TRUE),
    Common_trade_policy = weighted.mean(Common_trade_policy, weight, na.rm = TRUE),
    `Trade balance of goods` = mean(`Trade balance of goods`, na.rm = TRUE),
    `FDI net balance` = mean(`FDI net balance`, na.rm = TRUE),
    `Ratio of migrant to native workers` = mean(`Ratio of migrant to native workers`, na.rm = TRUE),
    .groups = "drop")

eu_proposals_pseudo_panel_aggregated <- eu_proposals_pseudo_panel_aggregated %>%
  mutate(
    Trade_balance_scaled = `Trade balance of goods` / 1e6,
    FDI_net_balance_scaled = `FDI net balance` / 1e6)

eu_proposals_pseudo_panel_data <- pdata.frame(eu_proposals_pseudo_panel_aggregated, index = c("cohort_id", "Year"))

eu_proposals_pseudo_panel_data <- eu_proposals_pseudo_panel_data |>
  mutate(Year = as.numeric(as.character(Year)))
```
```{r, echo=FALSE}
pseudo_var_names <- c(
  "Trade_balance_scaled" = "Trade balance of goods (billions)",
  "FDI_net_balance_scaled" = "FDI net balance (billions)",
  "Ratio.of.migrant.to.native.workers" = "Migrant to native workers ratio",
  "EU_enlargement_2004" = "EU enlargement (2004)",
   "EU_enlargement_2007" = "EU enlargement (2007)",
   "EU_enlargement_2013" = "EU enlargement (2013)",
   "Brexit_2020" = "Brexit (2020) / COVID-19",
   "Eurozone_crisis" = "Euro area sorevereign debt crisis (2010-2012)",
   "Annexation_of_Crimea" = "Annexation of Crimea by Russia (2014)",
   "Refugee_crisis" = "Refugee crisis (2015)",
   "COVID_pandemic" = "COVID-19 (2020-2021)",
   "Invasion_of_Ukraine" = "Russian invasion of Ukraine (2022)",
   "Nationalism_vote_share" = "Nationalist parties' vote share in parliamentary elections",
   "Single_currency" = "Opposition to the single currency (Euro)",
   "Common_foreign_policy" = "Opposition to a common foreign policy",
   "Common_defence_policy" = "Opposition to a common defence policy",
   "Common_migration_policy" = "Opposition to a common migratory policy",
   "Common_trade_policy" = "Opposition to a common trade policy")
```

## Multicollinearity test
```{r, echo=FALSE}
model_pseudo_panel_lm <- lm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = pseudo_panel_data)

vif(model_pseudo_panel_lm)
```
## Euroscepticism pseudo-panel data model
```{r, echo=FALSE}
model_pseudo_panel <- plm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
model_pseudo_panel_fe <- plm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = pseudo_panel_data,
  model = "within",
  effect = "twoways")
```

### Attitudes towards the EU (Euroscepticism including controls)
```{r, echo=FALSE}
pseudo_panel_data <- pseudo_panel_data|>
  mutate(
    EU_enlargement_2004 = ifelse(Year >= 2004, 1, 0),
    EU_enlargement_2007 = ifelse(Year >= 2007, 1, 0),
    EU_enlargement_2013 = ifelse(Year >= 2013, 1, 0),
    Brexit_2020 = ifelse(Year >= 2020, 1, 0))

pseudo_panel_data <- pseudo_panel_data|>
  mutate(
    Eurozone_crisis = ifelse(Year >= 2010 & Year <= 2012, 1, 0),
    Annexation_of_Crimea = ifelse(Year == 2014, 1, 0),
    Refugee_crisis = ifelse(Year == 2015, 1, 0),
    COVID_pandemic = ifelse(Year >= 2020 & Year <= 2021, 1, 0),
    Invasion_of_Ukraine = ifelse(Year >= 2022, 1, 0))
```

## Euroscepticism pseudo-panel data model (controlling for EU enlargement)

### Multicollinearity test
```{r, echo=FALSE}
model_pseudo_panel_enlargement_lm <- lm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers
  + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = pseudo_panel_data)

vif(model_pseudo_panel_enlargement_lm)
```
```{r, echo=FALSE}
model_pseudo_panel_enlargement <- plm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")

modelsummary(model_pseudo_panel_enlargement)

```
### including interactions between explanatory and control variables

```{r, echo=FALSE}
model_pseudo_panel_enlargement_interac <- plm(
   euroscepticism ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```

## Euroscepticism pseudo-panel data model (controlling for EU critical events)
### Multicollinearity test
```{r, echo=FALSE}
model_pseudo_panel_critical_lm <- lm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers
  + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = pseudo_panel_data)

vif(model_pseudo_panel_critical_lm)
```
```{r, echo=FALSE}
model_pseudo_panel_critical <- plm(
  euroscepticism ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```
### including interactions between explanatory and control variables
```{r, echo=FALSE}
model_pseudo_panel_critical_interac <- plm(
   euroscepticism ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```
### Output: Regression Table 1
```{r, echo=FALSE}
modelsummary(
  list(
    "Baseline Model" = model_pseudo_panel,
    "Fixed Effects Model" = model_pseudo_panel_fe,
    "EU Enlargement Model" = model_pseudo_panel_enlargement,
    "Interaction Model" = model_pseudo_panel_enlargement_interac,
    "External Shocks Model" = model_pseudo_panel_critical,
    "Interaction Model" = model_pseudo_panel_critical_interac
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 1: Globalisation and Euroscepticism",
    output = "regression_table_1.tex"
  )
```
```{r, echo=FALSE}
waldtest(model_pseudo_panel_enlargement, model_pseudo_panel_enlargement_interac,
         vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
```
```{r, echo=FALSE}
waldtest(model_pseudo_panel_critical, model_pseudo_panel_critical_interac,
         vcov = function(x) vcovHC(x, type = "HC1", cluster = "group"))
```

### Attitudes towards the EU (EU considered not benefitial)

### The EU considered not-benefitial pseudo-panel data model

```{r, echo=FALSE}
model_not_benefit_pseudo_panel <- plm(
  EU_not_benefit ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
model_not_benefit_pseudo_panel_fe <- plm(
  EU_not_benefit ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = pseudo_panel_data,
  model = "within",
  effect = "twoways")
```
## The EU considered not-benefitial pseudo-panel data model (controlling for EU enlargement)
```{r, echo=FALSE}
model_not_benefit_pseudo_panel_enlargement <- plm(
   EU_not_benefit ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```

## The EU considered not-benefitial pseudo-panel data model (controlling for EU critical events)
```{r, echo=FALSE}
model_not_benefit_pseudo_panel_critical <- plm(
   EU_not_benefit ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```
### including interactions between explanatory and control variables
```{r, echo=FALSE}
model_not_benefit_pseudo_panel_enlargement_interac <- plm(
   EU_not_benefit ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```
### including interactions between explanatory and control variables
```{r, echo=FALSE}
model_not_benefit_pseudo_panel_critical_interac <- plm(
   EU_not_benefit ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = pseudo_panel_data,
  model = "within",
  effect = "individual")
```
### Output: Regression Table 2
```{r, echo=FALSE}
modelsummary(
  list(
    "Baseline Model" = model_not_benefit_pseudo_panel,
    "Fixed Effects Model" = model_not_benefit_pseudo_panel_fe,
    "EU Enlargement Model" = model_not_benefit_pseudo_panel_enlargement,
    "Interaction Model" = model_not_benefit_pseudo_panel_enlargement_interac,
    "External Shocks Model" = model_not_benefit_pseudo_panel_critical,
    "Interaction Model" = model_not_benefit_pseudo_panel_critical_interac
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 2: Globalisation and Perception of the European Union as not beneficial",
    output = "regression_table_2.tex"
  )
```
### Attitudes towards EU common policies

## Opposition to the single currency (Euro)
```{r, echo=FALSE}
model_pseudo_panel_currency <- plm(
  Single_currency ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
fe_model_pseudo_panel_currency <- plm(
  Single_currency ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "twoways")
```
## Opposition to a common foreign policy
```{r, echo=FALSE}
model_pseudo_panel_foreign <- plm(
  Common_foreign_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
fe_model_pseudo_panel_foreign <- plm(
  Common_foreign_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "twoways")
```
## Opposition to a common defence policy
```{r, echo=FALSE}
model_pseudo_panel_defence <- plm(
  Common_defence_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
fe_model_pseudo_panel_defence <- plm(
  Common_defence_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "twoways")
```
## Opposition to a common migratory policy
```{r, echo=FALSE}
model_pseudo_panel_migration <- plm(
  Common_migration_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
fe_model_pseudo_panel_migration <- plm(
  Common_migration_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "twoways")
```
## Opposition to a common trade policy
```{r, echo=FALSE}
model_pseudo_panel_trade <- plm(
  Common_trade_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "pooling")
```
```{r, echo=FALSE}
fe_model_pseudo_panel_trade <- plm(
  Common_trade_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "twoways")
```
```{r, echo=FALSE}
setNames(
  list(
    model_pseudo_panel_currency,
    model_pseudo_panel_foreign,
    model_pseudo_panel_defence,
    model_pseudo_panel_migration,
    model_pseudo_panel_trade),
  c(
    "Single currency", 
    "Common foreign policy", 
    "Common defence policy", 
    "Common migratory policy", 
    "Common trade policy"))|>
msummary(
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r2.within", "r.squared", "adj.r.squared"),
  output = "EU_proposals.html")
```
```{r, echo=FALSE}
model_list <- list(
  "Single Currency" = model_pseudo_panel_currency,
  "Common Foreign Policy" = model_pseudo_panel_foreign,
  "Common Defence Policy" = model_pseudo_panel_defence,
  "Common Migration Policy" = model_pseudo_panel_migration,
  "Common Trade Policy" = model_pseudo_panel_trade
)

modelsummary(
  model_list,
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 3: Globalisation and Opposition to Common European Policies (Baseline)",
  output = "regression_table_3.tex"
)
```
```{r, echo=FALSE}
fe_model_list <- list(
  "Single Currency" = fe_model_pseudo_panel_currency,
  "Common Foreign Policy" = fe_model_pseudo_panel_foreign,
  "Common Defence Policy" = fe_model_pseudo_panel_defence,
  "Common Migration Policy" = fe_model_pseudo_panel_migration,
  "Common Trade Policy" = fe_model_pseudo_panel_trade
)

modelsummary(
  fe_model_list,
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 4: Globalisation and Opposition to Common European Policies (Fixed Effects)",
  output = "regression_table_4.tex"
)
```
```{r, echo=FALSE}
eu_proposals_pseudo_panel_data <- eu_proposals_pseudo_panel_data|>
  mutate(
    EU_enlargement_2004 = ifelse(Year >= 2004, 1, 0),
    EU_enlargement_2007 = ifelse(Year >= 2007, 1, 0),
    EU_enlargement_2013 = ifelse(Year >= 2013, 1, 0),
    Brexit_2020 = ifelse(Year >= 2020, 1, 0))

eu_proposals_pseudo_panel_data <- eu_proposals_pseudo_panel_data|>
  mutate(
    Eurozone_crisis = ifelse(Year >= 2010 & Year <= 2012, 1, 0),
    Annexation_of_Crimea = ifelse(Year == 2014, 1, 0),
    Refugee_crisis = ifelse(Year == 2015, 1, 0),
    COVID_pandemic = ifelse(Year >= 2020 & Year <= 2021, 1, 0),
    Invasion_of_Ukraine = ifelse(Year >= 2022, 1, 0))
```
## Opposition to the single currency (Euro) (controlling for EU enlargement)
```{r, echo=FALSE}
model_pseudo_panel_currency_enlargement <- plm(
  Single_currency ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_currency_enlargement_interac <- plm(
  Single_currency ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common foreign policy (controlling for EU enlargement)
```{r, echo=FALSE}
model_pseudo_panel_foreign_enlargement <- plm(
  Common_foreign_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_foreign_enlargement_interac <- plm(
  Common_foreign_policy ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common defence policy (controlling for EU enlargement)
```{r, echo=FALSE}
model_pseudo_panel_defence_enlargement <- plm(
  Common_defence_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_defence_enlargement_interac <- plm(
  Common_defence_policy ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common migratory policy (controlling for EU enlargement)
```{r, echo=FALSE}
model_pseudo_panel_migration_enlargement <- plm(
  Common_migration_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_migration_enlargement_interac <- plm(
  Common_migration_policy ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common trade policy (controlling for EU enlargement)
```{r, echo=FALSE}
model_pseudo_panel_trade_enlargement <- plm(
  Common_trade_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_trade_enlargement_interac <- plm(
  Common_trade_policy ~ Trade_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    FDI_net_balance_scaled * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020) +
    Ratio.of.migrant.to.native.workers * (EU_enlargement_2004 + EU_enlargement_2007 + EU_enlargement_2013 + Brexit_2020),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```

## Opposition to the single currency (Euro) (controlling for critical events)
```{r, echo=FALSE}
model_pseudo_panel_currency_critical <- plm(
  Single_currency ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_currency_critical_interac <- plm(
  Single_currency ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common foreign policy (controlling for critical events)
```{r, echo=FALSE}
model_pseudo_panel_foreign_critical <- plm(
  Common_foreign_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_foreign_critical_interac <- plm(
  Common_foreign_policy ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common defence policy (controlling for critical events)
```{r, echo=FALSE}
model_pseudo_panel_defence_critical <- plm(
  Common_defence_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_defence_critical_interac <- plm(
  Common_defence_policy ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common migratory policy (controlling for critical events)
```{r, echo=FALSE}
model_pseudo_panel_migration_critical <- plm(
  Common_migration_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_migration_critical_interac <- plm(
  Common_migration_policy ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
## Opposition to a common trade policy (controlling for critical events)
```{r, echo=FALSE}
model_pseudo_panel_trade_critical <- plm(
  Common_trade_policy ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers + Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine,
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
model_pseudo_panel_trade_critical_interac <- plm(
  Common_trade_policy ~ Trade_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    FDI_net_balance_scaled * (Eurozone_crisis + Annexation_of_Crimea + COVID_pandemic + Invasion_of_Ukraine) +
    Ratio.of.migrant.to.native.workers * (Eurozone_crisis + Annexation_of_Crimea + Refugee_crisis + COVID_pandemic + Invasion_of_Ukraine),
  data = eu_proposals_pseudo_panel_data,
  model = "within",
  effect = "individual")
```
```{r, echo=FALSE}
modelsummary(
  list(
    "Single Currency" = model_pseudo_panel_currency_enlargement,
    "Foreign Policy" = model_pseudo_panel_foreign_enlargement,
    "Defence Policy" = model_pseudo_panel_defence_enlargement,
    "Migration Policy" = model_pseudo_panel_migration_enlargement,
    "Trade Policy" = model_pseudo_panel_trade_enlargement
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 5: Globalisation and Opposition to Common European Policies\n(Controlling for EU Enlargement)",
  output = "regression_table_5.tex"
)
```
```{r, echo=FALSE}
modelsummary(
  list(
    "Single Currency" = model_pseudo_panel_currency_enlargement_interac,
    "Foreign Policy" = model_pseudo_panel_foreign_enlargement_interac,
    "Defence Policy" = model_pseudo_panel_defence_enlargement_interac,
    "Migration Policy" = model_pseudo_panel_migration_enlargement_interac,
    "Trade Policy" = model_pseudo_panel_trade_enlargement_interac
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 6: Globalisation and Opposition to Common European Policies (Controlling for EU Enlargement and Including Interaction Terms)",
  output = "regression_table_6.tex"
)
```
```{r, echo=FALSE}
modelsummary(
  list(
    "Single Currency" = model_pseudo_panel_currency_critical,
    "Foreign Policy" = model_pseudo_panel_foreign_critical,
    "Defence Policy" = model_pseudo_panel_defence_critical,
    "Migration Policy" = model_pseudo_panel_migration_critical,
    "Trade Policy" = model_pseudo_panel_trade_critical
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 7: Globalisation and Opposition to Common European Policies (Controlling for External Shocks)",
  output = "regression_table_7.tex"
)
```
```{r, echo=FALSE}
modelsummary(
  list(
    "Single Currency" = model_pseudo_panel_currency_critical_interac,
    "Foreign Policy" = model_pseudo_panel_foreign_critical_interac,
    "Defence Policy" = model_pseudo_panel_defence_critical_interac,
    "Migration Policy" = model_pseudo_panel_migration_critical_interac,
    "Trade Policy" = model_pseudo_panel_trade_critical_interac
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 8: Globalisation and Opposition to Common European Policies (Controlling for External Shocks and Including Interaction Terms)",
  output = "regression_table_8.tex"
)
```

### Nationalism vote share (15 countries)

```{r, echo=FALSE}
nationalism_vote_share <- read_csv("nationalism_vote_share.csv")
EU28_data_globalisation <- read_csv("EU28_data_globalisation.csv")

nationalism_vote_share_data <- nationalism_vote_share|>
left_join(EU28_data_globalisation, by = c("Country" = "Country", "Year" = "Year"))

nationalism_vote_share_data  <- nationalism_vote_share_data  %>%
  mutate(
    Trade_balance_scaled = `Trade balance of goods` / 1e6,
    FDI_net_balance_scaled = `FDI net balance` / 1e6)
```

```{r, echo=FALSE}
EU28_nationalism_vote_share <- read_csv("EU28_nationalism_vote_share.csv")
EU28_data_globalisation <- read_csv("EU28_data_globalisation.csv")

EU28_nationalism_vote_share_data <- EU28_nationalism_vote_share|>
left_join(EU28_data_globalisation, by = c("Country" = "Country", "Year" = "Year"))

EU28_nationalism_vote_share_data  <- EU28_nationalism_vote_share_data  %>%
  mutate(
    Trade_balance_scaled = `Trade balance of goods` / 1e6,
    FDI_net_balance_scaled = `FDI net balance` / 1e6)
```
```{r, echo=FALSE}
model_nationalism <- plm(Nationalism_vote_share ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
             data = nationalism_vote_share_data,
             index = c("Year", "Country"),
             model = "within",
             effect = "individual")
```
## Nationalism vote share 28 countries 
```{r, echo=FALSE}
EU28_model_nationalism <- plm(Nationalism_vote_share ~ Trade_balance_scaled + FDI_net_balance_scaled + Ratio.of.migrant.to.native.workers,
             data = EU28_nationalism_vote_share_data,
             index = c("Year", "Country"),
             model = "within",
             effect = "individual")
```
```{r, echo=FALSE}
modelsummary(
  list(
    "Nationalist Vote Share in 15 Countries" = model_nationalism,
    "Nationalist Vote Share in 28 Countries" = EU28_model_nationalism
  ),
  stars = TRUE,
  coef_map = pseudo_var_names,
  gof_map = c("nobs", "r.within", "r.squared", "adj.r.squared"),
  title = "Regression Table 9: Globalisation and Vote Share Received by Nationalist Parties in Parliamentary Elections",
  output = "regression_table_9.tex"
)
```
# Descriptive Statistics
```{r, echo=FALSE}
summary_data <- pseudo_panel_data[, c(3:7, 10:18)]

pseudo_var_names2 <- c(
  "Euroscepticism",
  "Perception of the EU as not beneficial",
  "Trade balance of goods (in millions USD)",
  "FDI net balance (in millions USD)",
  "Migrant to native workers ratio",
  "EU enlargement (2004)",
  "EU enlargement (2007)",
  "EU enlargement (2013)",
  "Brexit (2020) / COVID-19",
  "Euro area sovereign debt crisis (2010-2012)",
  "Annexation of Crimea by Russia (2014)",
  "Refugee crisis (2015)",
  "COVID-19 (2020-2021)",
  "Russian invasion of Ukraine (2022)")

summary_table <- data.frame(
  N = sapply(summary_data, function(x) sum(!is.na(x))),
  Min = sapply(summary_data, function(x) if(is.numeric(x)) min(x, na.rm = TRUE) else NA),
  Max = sapply(summary_data, function(x) if(is.numeric(x)) max(x, na.rm = TRUE) else NA),
  Mean = sapply(summary_data, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else NA),
  NAs = sapply(summary_data, function(x) sum(is.na(x))))

rownames(summary_table) <- pseudo_var_names2

summary_table[] <- lapply(summary_table, function(col) {
  if (is.numeric(col)) round(col, 3) else col
})
kable(summary_table, format = "latex", caption = "Summary Table 1: Euroscepticism") %>%
  kable_styling(
    bootstrap_options = c("hover"), # quitar "striped"
    font_size = 14,
    position = "center",
    full_width = FALSE
  )
latex_table <- kable(summary_table, format = "latex", booktabs = TRUE,
                     caption = "Summary Table 1: Euroscepticism") %>%
  kable_styling(latex_options = c("hold_position", "striped"))
save_kable(latex_table, file = "summary_table1.tex")
```
```{r, echo=FALSE}
summary_data2 <- eu_proposals_pseudo_panel_data[, c(3:10,13:21)]

pseudo_var_names2 <- c(
  "Single Currency",
  "Common Foreign Policy",
  "Common Defence Policy",
  "Common Migration Policy",
  "Common Trade Policy",
  "Trade balance of goods (in millions USD)",
  "FDI net balance (in millions USD)",
  "Migrant to native workers ratio",
  "EU enlargement (2004)",
  "EU enlargement (2007)",
  "EU enlargement (2013)",
  "Brexit (2020) / COVID-19",
  "Euro area sovereign debt crisis (2010-2012)",
  "Annexation of Crimea by Russia (2014)",
  "Refugee crisis (2015)",
  "COVID-19 (2020-2021)",
  "Russian invasion of Ukraine (2022)")

summary_table2 <- data.frame(
  N = sapply(summary_data2, function(x) sum(!is.na(x))),
  Min = sapply(summary_data2, function(x) if(is.numeric(x)) min(x, na.rm = TRUE) else NA),
  Max = sapply(summary_data2, function(x) if(is.numeric(x)) max(x, na.rm = TRUE) else NA),
  Mean = sapply(summary_data2, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else NA),
  NAs = sapply(summary_data2, function(x) sum(is.na(x))))

rownames(summary_table2) <- pseudo_var_names2

summary_table2[] <- lapply(summary_table2, function(col) {
  if (is.numeric(col)) round(col, 3) else col
})
kable(summary_table2, format = "latex", caption = "Summary Table 2: Opposition to Common European Policies") %>%
  kable_styling(
    bootstrap_options = c("hover"), # quitar "striped"
    font_size = 14,
    position = "center",
    full_width = FALSE
  )
latex_table <- kable(summary_table2, format = "latex", booktabs = TRUE,
                     caption = "Summary Table 2: Euroscepticism") %>%
  kable_styling(latex_options = c("hold_position", "striped"))
save_kable(latex_table, file = "summary_table2.tex")
```
```{r, echo=FALSE}
summary_data3 <- EU28_nationalism_vote_share_data[, c(3:6)]

pseudo_var_names3 <- c(
  "Nationalism Vote Share",
  "Trade balance of goods (in millions USD)",
  "FDI net balance (in millions USD)",
  "Migrant to native workers ratio")

summary_table3 <- data.frame(
  N = sapply(summary_data3, function(x) sum(!is.na(x))),
  Min = sapply(summary_data3, function(x) if(is.numeric(x)) min(x, na.rm = TRUE) else NA),
  Max = sapply(summary_data3, function(x) if(is.numeric(x)) max(x, na.rm = TRUE) else NA),
  Mean = sapply(summary_data3, function(x) if(is.numeric(x)) mean(x, na.rm = TRUE) else NA),
  NAs = sapply(summary_data3, function(x) sum(is.na(x))))

rownames(summary_table3) <- pseudo_var_names3

summary_table3[] <- lapply(summary_table3, function(col) {
  if (is.numeric(col)) round(col, 3) else col
})
kable(summary_table3, format = "latex", caption = "Summary Table 3: Electoral Support for Nationalist Parties") %>%
  kable_styling(
    bootstrap_options = c("hover"), # quitar "striped"
    font_size = 14,
    position = "center",
    full_width = FALSE
  )
latex_table <- kable(summary_table3, format = "latex", booktabs = TRUE,
                     caption = "Summary Table 3: Electoral Support for Nationalist Parties") %>%
  kable_styling(latex_options = c("hold_position", "striped"))
save_kable(latex_table, file = "summary_table3.tex")
```

